Optogenetic Maxwell Demon to Exploit Intrinsic Noise and Control Cell Differentiation Despite Time Delays and Extrinsic Variability

### 2023-02-01 paper.tex
Change figure 1 caption -- request changes to figure layout.

\section{Introduction}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{CartoonAndControler.png}
\caption{(A) Schematic of the T7 optogenetic control system (adapted from \cite{May2021}). A microscope observer is partially (PAC) or fully (FAC) aware  of cells; the resulting controller modulates a single spatially homogeneous light signal that perturbs all cells equally seeks to drive each genetically identical cells to a different, specified states. (B) Schematic of the optogenetically controllable T7 polymerase model, which is identical in all cells: Light activates the T7 polymerase-based production of protein, and the protein self-actuates its own production. (C) The FAC (top) and PAC (bottom) control laws for two cells ($\mathbf{u}^{XAC}(x_1,x_2)$ shown on left) break the symmetry between Cell 1 and Cell 2 and result in distinct marginal distributions for the cells' responses (right).}
\label{cartoons}
\end{center}
\vspace{-0.3in}
\end{figure}

>>>>

\section{Introduction}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{CartoonAndControler.png}
\caption{{\bf Optogenetic control of multiple cells using a single light course}
({\bf A}) Schematic of the gene expression system. UV light activates T7 polymerase based transcription and protein expression from the first promoter-gene construct, and the protein actuates its own production via a second promoter-gene construct.
({\bf B}) Schematic of the optogenetic control system. An observer is partially (PAC) or fully (FAC) aware of cell expression. The controller modulates a single spatially homogeneous light signal in attempt to drive each genetically identical cell to its own specified state.  
({\bf C}) The FAC (top) and PAC (bottom) control laws for two cells ($\mathbf{u}^{XAC}(x_1,x_2)$ shown on left) break the symmetry between Cell 1 and Cell 2 and result in distinct marginal distributions for the cells' responses (right).
Figure adapted from \cite{May2021}.}
\label{cartoons}
\end{center}
\vspace{-0.3in}
\end{figure}
% XXX - Please modify figure as follows: (1) switch panels A and B to match caption. (2) Change title of panel B (previously panel A) to "External Observer, controller and actuator".  (3) Change title of panel A (previously panel B) to "Internal gene regulation pathway". (4) Change title of panel C to "Feedback control law and resulting performance"
